---
title: "Finance Project Report"
author: | 
  |
  |
  | BT2201 Business Concepts and Metrics for Analytics
  | Semester 1, Academic Year 2022/2023
  |
  |
  |
  | Group #11
  | Fan Kai Jie, A0233048L
  | Fiona Xiao Jingyi, A0240290R
  | Ong Yong Chein, A0235421R
  | Ryan Koh Fang Rong, A0233182M
  | Shayer Ahmed, A0150756A
  |  
output: 
  pdf_document: default
  #html_document: default
---

```{r setup and file input, include=FALSE, warnings=FALSE}
library(readxl)
#library(PerformanceAnalytics)
#library(quantmod)
library(xts)
library(zoo)
library(tidyverse)
library(dplyr)
#library(PortfolioAnalytics)
library(psych)
library(fPortfolio)
#library(tidyquant)
#library(data.table)
library(knitr)
#library(kableExtra)
#library(scales)
library(ggplot2)
#library(timetk)
#library(plotly)
#library(broom)
#library(quadprog)
#library(NMOF)
options(warn=-1)
ETFfxReturns <- read_excel("ETFfxReturns.xlsx")
#View(ETFfxReturns)
ETFfxReturns_Sheet3 <- read_excel("ETFfxReturns_Sheet3.xlsx")
#View(ETFfxReturns_Sheet3)
ETFfxReturns_Sheet2 <- read_excel("ETFfxReturns_Sheet2.xlsx")
#View(ETFfxReturns_Sheet2)
```

\newpage

## Introduction
## 1 Introduction
## In this project, we have proposed 3 portfolios of ETFs in which we believe a typical Japanese retailer is able to invest comfortably. Taking into account the fact that not all investors have the same level of risk appetite and investment strategy, our 3 portfolios are differentiated according to their risk levels of low, medium, and high risk.

## Our portfolio consists of 16 ETFs from both Japan and the United States. This allows the retail investor exposure to a larger range of securities beyond just their domestic ones.

## We decided to use a 10.5-year period for our calculations, from October 2001 to March 2022.

## We have converted the returns of our ETFs from USD to express them in terms of JPY, such that it would be easier for Japanese investors to gauge their value.

## For our risk-free rate, we are using 0.1%. We obtained this figure by calculating its annualized geometric mean over the period mentioned above.

## The market risk premium is calculated to be at 6%. We obtained this figure similarly by calculating its annualized geometric mean over the same period mentioned above.

## 2 Our Selected List of ETFs
## The table below shows our chosen list of 16 ETFs. They were chosen based on their fees, liquidity (i.e. bid-ask spread, book-to-market ratio, as well as their tracking error values.

## We have also included a table calculating the geometric mean, variance, and standard deviation values of the individual ETFs’ returns over the defined period.

## 2 Our Selected List of ETFs
## The table below shows our chosen list of ETFs, as well as their geometric mean, variance, and standard deviation values over the defined period.
```{r mean and variance of return, echo=FALSE}
#Book-to-market ratio
NAV <- c(94.23, 51.67, 73.74, 47.51, 57.39, 2040.23, 345.69, 200.83, 98.29, 51.15, 37.11, 2088.84, 81.65, 38.22, 31.78, 27.30) #NAV obtained from etf.com
mkt_cap <- cbind(ETFfxReturns_Sheet2[,8], NAV) %>% mutate(BM = `Mkt Cap` / NAV)

BM_table <- cbind(ETFfxReturns_Sheet2[,8], NAV) %>% mutate(NAV = ifelse(rownames(ETFfxReturns_Sheet2) %in% c(6,12), NAV, NAV * 145.6630)) %>% mutate(BM = `Mkt Cap` / NAV) #USDJPY on close of 8 Nov 2022 was 145.6630.
BM <- BM_table$BM

#Tracking error
TE <- c(0.12, 5.39, 3.44, 3.55, 8.30, NA, 0.02, 4.52, 4.12, 8.19, 11.63, NA, 11.66, 9.17, 22.78, 0.29)

#ETF Characteristics Table
ETF_characteristics <- cbind(ETFfxReturns_Sheet2[,1], ETFfxReturns_Sheet2[,2], ETFfxReturns_Sheet2[,4], ETFfxReturns_Sheet2[,6], ETFfxReturns_Sheet2[,7], ETFfxReturns_Sheet2[,10], BM, TE) %>% rename("Liquidity" = "B/A Spread")
kable(ETF_characteristics)

#Number of rows and columns in the Dataset
nrow.rets <- nrow(ETFfxReturns)
ncol.rets <- ncol(ETFfxReturns)
#ETFfxReturns$mkt <- (1 + ETFfxReturns$mkt)*(1 + ETFfxReturns_Sheet3$USDJPY.Curncy) - 1
#ETFfxReturns$`AGG US Equity` <- (1 + ETFfxReturns$`AGG US Equity`)*(1 + ETFfxReturns_Sheet3$USDJPY.Curncy) - 1
#Unhedged return from USD to JPY
#Check with Prof again
for(i in 1:ncol.rets) {
  if (i!=1 & i!= 3 & i!= 9 & i!= 15){
    ETFfxReturns[,i] <- (1 + ETFfxReturns[,i]) * 
      (1 + ETFfxReturns_Sheet3$USDJPY.Curncy) - 1
  }
}
#Number of trading days
#check with prof again
number.of.days <- 252
#Calculating historical geometric mean
historical.geometric.mean <- data.frame(
  matrix(ncol = ncol.rets-1, 
         nrow = 1))
for (i in 1:(ncol.rets-1)) { 
  base = 1; 
  for (j in 1:nrow.rets) {
      base = base * (1+ETFfxReturns[j, i+1])
  }
  geo.mean = base^(1/nrow.rets)-1
  historical.geometric.mean[1, i] = geo.mean
}
annualised.hist.geo.mean = 
  (1 + historical.geometric.mean)^number.of.days - 1
colnames(annualised.hist.geo.mean) = colnames(ETFfxReturns)[-1]
##Calculating historical variance
historical.var <- data.frame(
  matrix(ncol = ncol.rets - 1, 
         nrow = 1))
for (i in 1:(ncol.rets-1)) { 
  historical.var[1, i] = 
    var(ETFfxReturns[,i+1])
}
annualised.hist.var = number.of.days * historical.var
colnames(historical.var) = colnames(ETFfxReturns)[-1]
colnames(annualised.hist.var) = colnames(ETFfxReturns)[-1]
#Calculating historical sd
annualised.hist.sd = annualised.hist.var^(0.5)
annualised.hist.geo.mean
annualised.hist.var
annualised.hist.sd
#Change the label for mkt and rf
kable(annualised.hist.geo.mean)
kable(annualised.hist.var)
kable(annualised.hist.sd)
```

```{r Calculation of beta, echo=FALSE}
## Calculation of beta
covariance.with.market <- data.frame(
  matrix(ncol = ncol.rets-3, 
         nrow = 1))
for (i in 1:(ncol.rets-3)) { 
  covariance.with.market[1, i] = 
    #cov(ETFfxReturns[,i+3]-ETFfxReturns$rf, 
    #ETFfxReturns[,2]-ETFfxReturns$rf)
    cov(ETFfxReturns[,i+3], ETFfxReturns[,2])
}
#Beta = covariance(i, market)/variance(market)
beta.df = covariance.with.market/var(ETFfxReturns$mkt)
#beta.df = covariance.with.market/var(ETFfxReturns$mkt -ETFfxReturns$rf)
colnames(beta.df) = colnames(ETFfxReturns)[-(1:3)]
#Demonstrate that linear regression gives the same results
(lmobj.AGG = lm((`AGG US Equity` )~(`mkt`), data = ETFfxReturns))
(lmobj.VSS = lm((`VSS US Equity` )~(`mkt`), data = ETFfxReturns))
#These betas are the same. 
#Calculating Merrill Lynch Beta 
merrill.lynch.beta.df = (2/3)*beta.df + (1/3)
#Display merrill lynch beta
#Calculating expected return from betas
#Calculate using the mean of what he suggested and from those two websites
#Future.annualised.risk.free.rate = 0.001697914. we will look
#back at history and take the rate.
annualised.market.risk.premium = mean(0.06, 0.0746, 0.0494)
future.annualised.risk.free.rate = 0.001697914
annualised.expected.miu = 
  future.annualised.risk.free.rate + 
  beta.df * annualised.market.risk.premium
colnames(annualised.expected.miu) = colnames(ETFfxReturns)[-(1:3)]
#Calculating the covariance matrix
covariance.matrix = cov(ETFfxReturns[,-(1:3)])
#covariance.matrix2 = var(ETFfxReturns[,-(1:3)])
annualised.covariance.matrix = covariance.matrix * number.of.days
#annualised.covariance.matrix2 = covariance.matrix * sqrt(number.of.days)
```

```{r plotting the frontier, echo=FALSE}
#Now we have the expected miu and covariance matrix, 
#we can plot the frontier
#Simulate the returns to give the desired stats
B <- array(rnorm(nrow(annualised.covariance.matrix)+1 *
                   nrow(annualised.covariance.matrix)),
           dim = c(nrow(annualised.covariance.matrix)+1,
                   nrow(annualised.covariance.matrix)))
B <- B %*% backsolve(chol(cov(B)),
                     diag(1, nrow(annualised.covariance.matrix)))
B <- t(B) - colMeans(B)
B <- B / apply(B, 1, sd)
B <- t(B)
#round(apply(B, 2, sd), 10)
## [1] 1 1 1 1 1
#round(apply(B, 2, mean), 10)
## [1] 0 0 0 0 0
#round(cov(B), 10)
B <- B %*% chol(annualised.covariance.matrix)
B <- t(B) + unlist(annualised.expected.miu)
B <- t(B)
#check
all.equal(cov(B), annualised.covariance.matrix)
all.equal(colMeans(B), unlist(annualised.expected.miu))
Spec <- portfolioSpec()
Spec.rf <- Spec
setRiskFreeRate(Spec) <- future.annualised.risk.free.rate
setRiskFreeRate(Spec.rf) <- future.annualised.risk.free.rate
simulate.ts <- ts(B)
myret <- as.timeSeries(simulate.ts)
mymvf <- portfolioFrontier(myret, Spec, constraints = "LongOnly")
frontierPlot(mymvf)
grid()
tangencyLines(mymvf)
tailoredFrontierPlot(mymvf)
```
### We have modified the weights to create 3 different portfolios to cater to investors with different risk appetites.
### The first portfolio will be the Global Minimum Variance Portfolio(GVMP) the portfolio with the lowest Risk. 
### It is weighted to give the least risk out of our holdings, catering to investors whose preferences lie in safe investments with minimal risk.

```{r GMVP, echo=FALSE}
#Portfolio with the lowest Risk - Global Minimum Variance Portfolio
gmvP <- minvariancePortfolio(myret, Spec, constraints = "maxW[1:16] = 0.4")
gmv.w <- getWeights(gmvP)
#Pie chart of the weights for the GMVP
weightsPie(gmvP, box = FALSE)
weights1 <- data.frame(gmv.w)
gmvpW1_draft <- subset(weights1, gmv.w*100 > 0.001)
assets <- colnames(getWeights(mymvf))
assets_names <- row.names(gmvpW1_draft)
#Bar plot
ggplot(data= gmvpW1_draft , aes(x=assets_names , y=gmv.w, fill=assets_names)) +
  geom_bar(stat="identity", position=position_dodge(),colour="black") +
  geom_text(aes(label=sprintf("%.02f %%",gmv.w*100)),
            position=position_dodge(width=0.9), vjust=-0.25, check_overlap = TRUE) +
  ggtitle("Minimum Variance Portfolio Optimal Weights")+ theme(plot.title = element_text(hjust = 0.5)) +
  labs(x= "Assets", y = "Weight (%)") +
  guides(fill = guide_legend(title = "Assets"))

###############################################
#Pie Chart for GMVP
colour <- rainbow(8)
piepercent <- assets_names %>% 
  paste(",",sep ="") %>% 
  paste(100*as.vector(unlist(gmvpW1_draft))) %>% 
  paste("%",sep = "")

pie(as.vector(unlist(gmvpW1_draft)), labels = piepercent, main = "Piechart of GMVP portfolio weights", col = colour)
#legend("topright",assets_draft, cex = 1, fill = colour, title = "Assets", bg='lightblue')
```

```{r Tangent Portfolio, echo=FALSE}
#Tangency portfolio - HighestSharpe's Slope
tanP <- tangencyPortfolio(myret, Spec.rf, constraints = "maxW[-c(6, 1, 4, 3,10, 14, 7, 5)]=0.00" )
# get weights for tangency portfolio
tan.w <- round(getWeights(tanP), 3)
#Pie chart of the weights for the Tangency Portfolio
weightsPie(tanP, box = FALSE)
tanwt1 <- data.frame(tan.w)
tanwt1_draft <- subset(tanwt1, tan.w*100 > 0.001)
assets_draft <- row.names(tanwt1_draft)
#Bar plot
ggplot(data=tanwt1_draft, aes(x=assets_draft, y=tan.w, fill=assets_draft)) +
  geom_bar(stat="identity", position=position_dodge(),colour="black") +
  geom_text(aes(label=sprintf("%.02f %%",tan.w*100)),
            position=position_dodge(width=0.9), vjust=-0.25, check_overlap = TRUE) +
  ggtitle("Tangency Portfolio Optimal Weights")+ theme(plot.title = element_text(hjust = 0.5)) +
  labs(x= "Assets", y = "Weight (%)") +
  guides(fill = guide_legend(title = "Assets"))
#Pie Chart
ggplot(tanwt1_draft, aes(x="", y=tan.w, fill=assets_draft)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0) +
  theme_void() +
  geom_text(aes(label = tan.w), color = "black", size= 5,position = position_stack(vjust = 0.5)) +
  scale_fill_brewer("Pastel1") +
  ggtitle("MaxP Portfolio Optimal Weights") +
  guides(fill = guide_legend(title = "Assets"))
  
##################################
#Pie Chart for Tangency Portfolio
colour <- rainbow(8)
piepercent <- assets_draft %>% 
  paste(",",sep ="") %>% 
  paste(100*as.vector(unlist(tanwt1_draft))) %>% 
  paste("%",sep = "")

pie(as.vector(unlist(tanwt1_draft)), labels = piepercent, main = "Piechart of tangency portfolio weights", col = colour)
#legend("top",assets_draft, cex = 0.5, fill = colour, title = "Assets", bg='lightblue')
```


```{r MaxP Portfolio, echo=FALSE}
Spec.Obj.risk <- Spec
setType(Spec.Obj.risk) = "CVaR"
# Set type Variance
setSolver(Spec.Obj.risk) = "solveRglpk.CVAR"
# Solver method to be used to resolve weights
setTargetRisk(Spec.Obj.risk) <- 0.3
# Maximum Return Portfolio
maxP <- maxreturnPortfolio(myret, Spec.Obj.risk)
max.w <- getWeights(maxP)
# max.w
weightsPie(maxP, box = FALSE)
maxPW1 <- data.frame(max.w)
ggplot(data=maxPW1, aes(x=assets, y=max.w, fill=assets)) +
  geom_bar(stat="identity", position=position_dodge(),colour="black") +
  geom_text(aes(label=sprintf("%.02f %%",max.w*100)),
            position=position_dodge(width=0.9), vjust=-0.25, check_overlap = TRUE) +
  ggtitle("MaxP Portfolio Optimal Weights")+ theme(plot.title = element_text(hjust = 0.5)) +
  labs(x= "Assets", y = "Weight (%)")
  
####################################
#Pie Chart for MaxP
ret2 = ETFfxReturns[,-(1:3)]  #excluding dates
mu1 = t(annualised.hist.geo.mean)[-c(1,2),]#colMeans(ret2)  #mean returns
na1 = ncol(ret2)  #number of assets
varc1 = cov(ret2)


riskp1 = NULL  #vector to store risk
retp1 = NULL  #vector to store returns

w = c(0,0,0,8.4087, 16.2471, 5.0822, 48.3172, 4.7284, 0,4.2494, 3.1067, 0,0, 9.8862,0,0)  #max p weights
r1 = t(w) %*% mu1 #t(annualised.hist.geo.mean)[-c(1,2),]   #matrix multiplication
sd1 = t(w) %*% annualised.covariance.matrix %*% w #t(w) %*% varc1 %*% w
retp1 = rbind(retp1, r1)
riskp1 = rbind(riskp1, sqrt(sd1))

#list of ETFs
maxP.ETFs <- c("BNDX US Equity", "VWOB US Equity", "1306 JT Equity", "VOO US Equity", "VO US Equity", "VGK US Equity", "VWO US Equity", "VNQI US Equity")

#Weightage of ETFS
maxP.weights <-  c(8.4, 16.2, 5.1, 48.3, 4.7, 4.3, 3.1, 9.9)

colour <- rainbow(8)
piepercent <- maxP.ETFs %>% 
  paste(",",sep ="") %>% 
  paste(maxP.weights) %>% 
  paste("%",sep = "")

pie(maxP.weights, labels = piepercent, main = "Piechart of MaxP portfolio weights", col = colour)
#legend("top",assets_draft, cex = 0.5, fill = colour, title = "Assets", bg='lightblue')

```


Trying to get the different weighted porfolios

first up ewP

```{r ewp2}
ewSpec <- Spec
setWeights(ewSpec) <- rep(1/(ncol.rets - 3), times = (ncol.rets-3))
ewP <- feasiblePortfolio(myret, spec = ewSpec, constraints = "LongOnly")
getTargetReturn(ewP)
getTargetRisk(ewP)
ewP@portfolio@portfolio$weights
ewPdf <- as.data.frame(ewP@portfolio@portfolio$weights) %>% rename(weights = `ewP@portfolio@portfolio$weights`) 
ewPdf <- ewPdf %>% mutate(Assets = rownames(ewPdf)) 
ggplot(ewPdf, aes(x = Assets, y = weights, fill = Assets))  + geom_bar(stat = "identity")+ theme_classic() + coord_flip() + theme(legend.position = "none", panel.grid.major = element_blank()) 
```

next min variance portfolio

```{r min variance}
# this is if we didnt force the min to 1.5. Also i realsied ryan alr did this oops 
mvP <- minvariancePortfolio(myret, spec = Spec, constraints = "minW[1:16] = 0.015")
getTargetReturn(mvP)
getTargetRisk(mvP)
mvP@portfolio@portfolio$weights
mvPdf <- as.data.frame(mvP@portfolio@portfolio$weights) %>% rename(weights = `mvP@portfolio@portfolio$weights`) 
mvPdf <- mvPdf %>% mutate(Assets = rownames(mvPdf)) 
ggplot(mvPdf, aes(x = Assets, y = weights, fill = Assets)) + geom_bar(stat = "identity") + theme_classic() + theme(legend.position = "none", panel.grid.major = element_blank()) + coord_flip() 
```

```{r sharpe plot}
np1 = 200  #number of portfolios
ret2 = ETFfxReturns[,-(1:3)]  #excluding dates
mu1 = colMeans(ret2)  #mean returns
na1 = ncol(ret2)  #number of assets
varc1 = cov(ret2)
riskp1 = NULL  #vector to store risk
retp1 = NULL  #vector to store returns
for (i in 1:np1) {
    w = diff(c(0, sort(runif(na1 - 1)), 1))  # random weights
    r1 = t(w) %*% mu1  #matrix multiplication
    sd1 = t(w) %*% varc1 %*% w
    retp1 = rbind(retp1, r1)
    riskp1 = rbind(riskp1, sd1)
}
# create a data frame of risk and return
d_p1 = data.frame(Ret = retp1, Risk = riskp1)
d_p1 = d_p1 %>% mutate(SharpeRatio = (Ret - 0.001697914) / Risk)
p1 = ggplot(d_p1, aes(Risk, Ret, colour = SharpeRatio))
# scatter plot
p1 = p1 + geom_point()
# scatter plot with density and identified port risk return (highest
# lowest returns and min risk)
p1 + geom_point() + geom_hline(yintercept = c(max(d_p1$Ret), median(d_p1$Ret),
    min(d_p1$Ret)), colour = c("darkgreen", "darkgray", "darkred"), size = 1) +
    geom_vline(xintercept = d_p1[(d_p1$Risk == min(d_p1$Risk)), ][, 2]) +
    labs(colour = "Sharpe Ratio", x = "Portfolio Risk", y = "Portfolio Return",
        title = "Random Feasible Portfolios") + theme_bw()
```

```{r ewP}
ewSpec <- Spec
setWeights(ewSpec) <- rep(1/(ncol.rets - 3), times = (ncol.rets-3))
ewP <- feasiblePortfolio(myret, spec = ewSpec, constraints = "LongOnly")
getTargetReturn(ewP)
getTargetRisk(ewP)
ewP@portfolio@portfolio$weights
ewPdf <- as.data.frame(ewP@portfolio@portfolio$weights) %>% rename(weights = `ewP@portfolio@portfolio$weights`) 
ewPdf <- ewPdf %>% mutate(Assets = rownames(ewPdf)) 
ggplot(ewPdf, aes(x = Assets, y = weights, fill = Assets))  + geom_bar(stat = "identity")+ theme_classic() + coord_flip() + theme(legend.position = "none", panel.grid.major = element_blank()) 
```

next min variance portfolio

```{r min variance2}
# this is if we didnt force the min to 1.5. Also i realsied ryan alr did this oops 
mvP <- minvariancePortfolio(myret, spec = Spec, constraints = "minW[1:16] = 0.015")
getTargetReturn(mvP)
getTargetRisk(mvP)
mvP@portfolio@portfolio$weights
mvPdf <- as.data.frame(mvP@portfolio@portfolio$weights) %>% rename(weights = `mvP@portfolio@portfolio$weights`) 
mvPdf <- mvPdf %>% mutate(Assets = rownames(mvPdf)) 
ggplot(mvPdf, aes(x = Assets, y = weights, fill = Assets)) + geom_bar(stat = "identity") + theme_classic() + theme(legend.position = "none", panel.grid.major = element_blank()) + coord_flip() 
```

```{r rebalancing}
gmvp.weights = data.frame(t(data.frame(getWeights(gmvP))))
starting = 1000
#252/12 = 21, we rebalance every 21 days 
cumulative.returns <- data.frame(
  matrix(ncol = ncol.rets-3, 
         nrow = nrow.rets+1))
cumulative.returns[1,] = 1000*gmvp.weights
#cumalative.return = t(cumulative.returns)
for(i in 1: nrow.rets) { 
  for (j in 1:16) { 
    cumulative.returns[i+1, j] = cumulative.returns[i, j] * 
      (1 + ETFfxReturns[i, j + 3])
  }
  if(i%%21 == 0) {
    sum1 = sum(cumulative.returns[i+1, ])
    cumulative.returns[i+1, ] = sum1*gmvp.weights
    }
}
```

\newpage
## Appendix



```{r USELESS CODE, echo=FALSE}
# #part 1
# expected.miu.vector = unlist(annualised.expected.miu)
# 
# p1 = mvFrontier(expected.miu.vector, 
#                     annualised.covariance.matrix, n = 50, 
#                     rf = NA)
# plot(y= object$returns, x= object$volatility)
# 
# object2 = mvFrontier(unlist(annualised.hist.geo.mean[,-(1:2)]), 
#                     annualised.covariance.matrix, n = 500, 
#                     rf = NA)
# plot(y= object2$returns, x= object2$volatility)
# 
# plot(y=expected.miu.vector, x=unlist(annualised.hist.sd[,-(1:2)]))
# 
# object3 = maxSharpe(annualised.expected.miu, annualised.covariance.matrix, future.annualised.risk.free.rate, -100)
# plot(y= object3$returns, x= object3$volatility)
# 
# maxSharpe(annualised.expected.miu-future.annualised.risk.free.rate, annualised.covariance.matrix,
# wmin = -Inf, wmax = Inf, method = "qp",
# groups = NULL, groups.wmin = NULL, groups.wmax = NULL)
# 
# plot(p1$volatility, p1$return, pch = 19, cex = 0.5, type = "o",
# xlab = "Expected volatility",ylab = "Expected return")
# lines(p2$volatility, p2$return, col = grey(0.5))
# 
# 
# 
# 
# 
# #Frontier plot
# nFunds <- ncol.rets - 3
# Spec <- portfolioSpec()
# mymvf <- portfolioFrontier(myret, Spec, constraints = "LongOnly")
# 
# 
# 
# 
# 
# 
# 
# 
# #Cumulative returns plot
# cumulative.return.plot = data.frame(
#   matrix(ncol = ncol.rets-1, 
#          nrow = nrow.rets))
# #cumulative.return.plot[1,] = 1
# 
# for (i in 1:(ncol.rets-1)) {
#   cumulative.return.plot[,i] = cumprod(1 + ETFfxReturns[,i+1])
# }
# colnames(cumulative.return.plot) = colnames(ETFfxReturns)[-1]
# cumulative.return.plot.xts = xts(cumulative.return.plot,
#                                  order.by = ETFfxReturns$x)
# plot(cumulative.return.plot.xts[,c(1,3)])
# 
# 
# 
# 
# 
# 
# 
# 
# 
# #calculate daily returns from annualised.expected.miu
# 
# #####neeed to double check this. do we even need daily return?!!!!!!!!!!!
# daily.expected.miu = ((annualised.expected.miu + 1)^(1/number.of.days))-1
# Exp.Ret = unlist(daily.expected.miu)
# 
# #monthly return
# #montly.expected.miu = 
# 
# ##annualised return
# Exp.Ret = unlist(annualised.expected.miu)
# 
# ## setEstimator(Spec)="CustMuSigHistEstimator"
# CustMuSigHistEstimator <- function(x, Spec = NULL, ...)
# {
#   #  Debug:  x.mat <- assets  x<-pf.data
#   stopifnot(inherits(x, "timeSeries"))
#   x.mat = getDataPart(x)  # Extract Matrix
#   if (is.null(Spec)) {
#     stop("Custom Estimator requires Expected Returns, see file main.R")
#   } else {
#     mu.input = Spec@model$param$Exp.Ret
#   }
#   # Estimate:
#   ## MU.Hist
#   ########
#   mu.Hist.m <- colMeans(x.mat)
#   ## SIGMA
#   ########
#   s2.Hist.m <- apply(x.mat, 2, var)
#   # risk.h <- sqrt(exp(2*12*log(1+mu.Hist.m))*(exp(12*log(s2.Hist.m/(1+mu.Hist.m)^2+1))-1))
#   risk.h.m <- sqrt(exp(2*log(1+mu.Hist.m))*(exp(log(s2.Hist.m/(1+mu.Hist.m)^2+1))-1))
#   rho.h <- cor(x.mat)  # No need the .m - correlations are not really time dependent, so to speak - scale free measure
#   cov.h.m <- diag(risk.h.m) %*% rho.h %*% diag(risk.h.m)
#   rownames(cov.h.m) <- colnames(cov.h.m) <- names(risk.h.m)
#   list(mu = mu.input, Sigma = cov.h.m)  # Return Value
# }
#  
# Spec <- portfolioSpec()
# { #  THESE LINES COMBINED TO USE CUSTOM ESTIMATOR
#   Spec@model$param$Exp.Ret <- Exp.Ret
#   setEstimator(Spec)="CustMuSigHistEstimator"
# }
# 
# setNFrontierPoints(Spec) <- 50
# ### need to change risk free rate
# setRiskFreeRate(Spec) <- future.annualised.risk.free.rate
# 
# xts.object.for.frontier = xts(ETFfxReturns[,-(1:3)], 
#                                  order.by = ETFfxReturns$x)
# ts.object.for.frontier = as.timeSeries(xts.object.for.frontier)
# 
# frontier.obj <- portfolioFrontier(ts.object.for.frontier, Spec, constraints = "LongOnly")
# frontierPlot(frontier.obj)
# grid()
# singleAssetPoints(frontier.obj)
# tangencyLines(frontier.obj)
```
