---
title: "Finance Project Report"
author: | 
  |
  |
  | BT2201 Business Concepts and Metrics for Analytics
  | Semester 1, Academic Year 2022/2023
  |
  |
  |
  | Group #11
  | Fan Kai Jie, A0233048L
  | Fiona Xiao Jingyi, A0240290R
  | Ong Yong Chein, A0235421R
  | Ryan Koh Fang Rong, A0233182M
  | Shayer Ahmed, A0150756A
  |  
output: 
  pdf_document: default
  #html_document: default
---

```{r setup and file input, include=FALSE, warnings=FALSE}
library(readxl)
library(xts)
library(zoo)
library(tidyverse)
library(dplyr)
library(psych)
library(fPortfolio)
library(knitr)
library(ggplot2)
library(ggfortify)
library(RColorBrewer)
library(psych)

options(warn=-1)
ETFfxReturns <- read_excel("ETFfxReturns.xlsx")
ETFfxReturns_Sheet3 <- read_excel("ETFfxReturns_Sheet3.xlsx")
ETFfxReturns_Sheet2 <- read_excel("ETFfxReturns_Sheet2.xlsx")
```

\newpage


## 1 Introduction
### In this project, we have proposed 3 portfolios of ETFs in which we believe a typical Japanese retailer is able to invest comfortably. Taking into account the fact that not all investors have the same level of risk appetite and investment strategy, our 3 portfolios are differentiated according to their risk levels of low, medium, and high risk.

### Our portfolio consists of 16 ETFs from both Japan and the United States. This allows the retail investor exposure to a larger range of securities beyond just their domestic ones.

### We decided to use a 10.5-year period for our calculations, from October 2001 to March 2022.

### We have converted the returns of our ETFs from USD to express them in terms of JPY, such that it would be easier for Japanese investors to gauge their value.

### For our risk-free rate, we are using 0.1%. We obtained this figure by calculating its annualized geometric mean over the period mentioned above.

### The market risk premium is calculated to be at 6%. We obtained this figure similarly by calculating its annualized geometric mean over the same period mentioned above.

## 2 Our Selected List of ETFs
### The table below shows our chosen list of 16 ETFs. They were chosen based on their fees, liquidity (i.e. bid-ask spread, book-to-market ratio, as well as their tracking error values.

```{r characteristic table, echo=FALSE}
#Book-to-market ratio
NAV <- c(94.23, 51.67, 73.74, 47.51, 57.39, 2040.23, 345.69, 200.83, 98.29, 51.15, 37.11, 2088.84, 81.65, 38.22, 31.78, 27.30) #NAV obtained from etf.com
mkt_cap <- cbind(ETFfxReturns_Sheet2[,8], NAV) %>% mutate(BM = `Mkt Cap` / NAV)
BM_table <- cbind(ETFfxReturns_Sheet2[,8], NAV) %>% mutate(NAV = ifelse(rownames(ETFfxReturns_Sheet2) %in% c(6,12), NAV, NAV * 145.6630)) %>% mutate(BM = `Mkt Cap` / NAV) #USDJPY on close of 8 Nov 2022 was 145.6630.
BM <- BM_table$BM
#Tracking error
TE <- c(0.12, 5.39, 3.44, 3.55, 8.30, NA, 0.02, 4.52, 4.12, 8.19, 11.63, NA, 11.66, 9.17, 22.78, 0.29)
#ETF Characteristics Table
ETF_characteristics <- cbind(ETFfxReturns_Sheet2[,1], ETFfxReturns_Sheet2[,2], ETFfxReturns_Sheet2[,4], ETFfxReturns_Sheet2[,6], ETFfxReturns_Sheet2[,7], ETFfxReturns_Sheet2[,10], BM, TE) %>% rename("Liquidity" = "B/A Spread")
kable(ETF_characteristics)
```


```{r historical stats, echo=FALSE}
#Number of rows and columns in the Dataset
nrow.rets <- nrow(ETFfxReturns)
ncol.rets <- ncol(ETFfxReturns)

#ETFfxReturns$mkt <- (1 + ETFfxReturns$mkt)*(1 + ETFfxReturns_Sheet3$USDJPY.Curncy) - 1
#ETFfxReturns$`AGG US Equity` <- (1 + ETFfxReturns$`AGG US Equity`)*(1 + ETFfxReturns_Sheet3$USDJPY.Curncy) - 1

#Unhedged return from USD to JPY
for(i in 1:ncol.rets) {
  if (i!=1 & i!= 3 & i!= 9 & i!= 15){
    ETFfxReturns[,i] <- (1 + ETFfxReturns[,i]) * 
      (1 + ETFfxReturns_Sheet3$USDJPY.Curncy) - 1
  }
}

#Number of trading days
number.of.days <- 252

#Calculating historical geometric mean
historical.geometric.mean <- data.frame(
  matrix(ncol = ncol.rets-1, 
         nrow = 1))
for (i in 1:(ncol.rets-1)) { 
  base = 1; 
  for (j in 1:nrow.rets) {
      base = base * (1+ETFfxReturns[j, i+1])
  }
  geo.mean = base^(1/nrow.rets)-1
  historical.geometric.mean[1, i] = geo.mean
}

annualised.hist.geo.mean = 
  (1 + historical.geometric.mean)^number.of.days - 1
colnames(annualised.hist.geo.mean) = colnames(ETFfxReturns)[-1]

##Calculating historical variance
historical.var <- data.frame(
  matrix(ncol = ncol.rets - 1, 
         nrow = 1))
for (i in 1:(ncol.rets-1)) { 
  historical.var[1, i] = 
    var(ETFfxReturns[,i+1])
}
annualised.hist.var = number.of.days * historical.var
colnames(historical.var) = colnames(ETFfxReturns)[-1]
colnames(annualised.hist.var) = colnames(ETFfxReturns)[-1]

#Calculating historical sd
annualised.hist.sd = annualised.hist.var^(0.5)
```

```{r Calculation of beta, echo=FALSE}
## Calculation of beta
covariance.with.market <- data.frame(
  matrix(ncol = ncol.rets-3, 
         nrow = 1))
for (i in 1:(ncol.rets-3)) { 
  covariance.with.market[1, i] = 
    cov(ETFfxReturns[,i+3], ETFfxReturns[,2])
}

#Beta = covariance(i, market)/variance(market)
beta.df = covariance.with.market/var(ETFfxReturns$mkt)
colnames(beta.df) = colnames(ETFfxReturns)[-(1:3)]

#Demonstrate that linear regression gives the same results
(lmobj.AGG = lm((`AGG US Equity` )~(`mkt`), data = ETFfxReturns))
(lmobj.VSS = lm((`VSS US Equity` )~(`mkt`), data = ETFfxReturns))
#These betas are the same. 

#Calculating Merrill Lynch Beta 
merrill.lynch.beta.df = (2/3)*beta.df + (1/3)

#Calculating expected return from betas
#Calculate using the mean of what he suggested and from those two websites
#Future.annualised.risk.free.rate = 0.001697914. we will look
#back at history and take the rate.
annualised.market.risk.premium = mean(0.06, 0.0746, 0.0494)
future.annualised.risk.free.rate = 0.001697914
annualised.expected.miu = 
  future.annualised.risk.free.rate + 
  beta.df * annualised.market.risk.premium
colnames(annualised.expected.miu) = colnames(ETFfxReturns)[-(1:3)]

#Calculating the covariance matrix
covariance.matrix = cov(ETFfxReturns[,-(1:3)])
annualised.covariance.matrix = covariance.matrix * number.of.days
```

```{r plotting the frontier, echo=FALSE}
#Now we have the expected miu and covariance matrix,we can plot the frontier

#Simulate the returns to give the desired stats
B <- array(rnorm(nrow(annualised.covariance.matrix)+1 *
                   nrow(annualised.covariance.matrix)),
           dim = c(nrow(annualised.covariance.matrix)+1,
                   nrow(annualised.covariance.matrix)))
B <- B %*% backsolve(chol(cov(B)),
                     diag(1, nrow(annualised.covariance.matrix)))
B <- t(B) - colMeans(B)
B <- B / apply(B, 1, sd)
B <- t(B)
#round(apply(B, 2, sd), 10)
## [1] 1 1 1 1 1
#round(apply(B, 2, mean), 10)
## [1] 0 0 0 0 0
#round(cov(B), 10)
B <- B %*% chol(annualised.covariance.matrix)
B <- t(B) + unlist(annualised.expected.miu)
B <- t(B)
#check
all.equal(cov(B), annualised.covariance.matrix)
all.equal(colMeans(B), unlist(annualised.expected.miu))


Spec <- portfolioSpec()
Spec.rf <- Spec
setRiskFreeRate(Spec) <- future.annualised.risk.free.rate
setRiskFreeRate(Spec.rf) <- future.annualised.risk.free.rate
simulate.ts <- ts(B)
myret <- as.timeSeries(simulate.ts)
mymvf <- portfolioFrontier(myret, Spec, constraints = "LongOnly")
gmvP <- minvariancePortfolio(myret, Spec)
tanP <- tangencyPortfolio(myret, Spec)
ewSpec <- Spec
setWeights(ewSpec) <- rep(1/(ncol.rets - 3), times = (ncol.rets-3))
ewP <- feasiblePortfolio(myret, spec = ewSpec, constraints = "LongOnly")
frontierPlot(mymvf)
tangencyPoints(mymvf, col= "blue", pch = 15)
equalWeightsPoints(mymvf, col = "dark green", pch = 15)
minvariancePoints(mymvf, col= "red", pch = 15)
grid()
tangencyLines(mymvf)
singleAssetPoints(mymvf, pch = 4)
legend(x = "topleft",
       legend=c("tanP", "ewP", "gmvP"), 
       fill = c("blue","dark green", "red"))
#legend(x= "bottomright", legend=c("Efficient Frontier", "ETF", "Specific Portfolio"), pch(1, 4, 15))
#legend()
#tailoredFrontierPlot(mymvf)



mymvf.returns = mymvf@portfolio@portfolio[["targetReturn"]]
portfolio.points = as.data.frame(mymvf.returns)
portfolio.points$sd = mymvf@portfolio@portfolio[["targetRisk"]][,1]
portfolio.points = portfolio.points[, c(1,3)]

ETF.mu = as.data.frame(t(annualised.expected.miu))
ETF.sd = as.data.frame(t(annualised.hist.sd[,-(1:2)]))
ETF.points = cbind(ETF.mu, ETF.sd)
colnames(ETF.points) = c("mean", "sd")
ETF.points$ETF = rownames(ETF.points)

#portfolio.points = cbind(portfolio.points, ETF.points)

#plot(x=portfolio.points$sd, y=portfolio.points$mean, data = portfolio.points)


#1 - GMVP
#2 - Tangency
#3 - EWP



# specific.points <- data.frame(
#   matrix(ncol = 2, nrow = 3))
# specific.points[1, 1] = getTargetReturn(gmvP)[1]
# specific.points[1, 2] = getTargetRisk(gmvP)[1]
# specific.points[2, 1] = getTargetReturn(tanP)[1]
# specific.points[2, 2] = getTargetRisk(tanP)[1]
# specific.points[3, 1] = getTargetReturn(ewP)[1]
# specific.points[3, 2] = getTargetRisk(ewP)[1]
# colnames(specific.points) = c("mean", "sd")
# specific.points$label = c("gmvP", "tanP", "ewP")
# 
# 
# #portfolio.points$ETF = c(rep(0, 50), 1:16, rep(0,3))
# #portfolio.points$Specific = c(rep(0,66), 1:3)
# 
# #portfolio.points$ETF = as.factor(portfolio.points$ETF)
# #portfolio.points$Specific = as.factor(portfolio.points$Specific)
# 
# 
# par(mar= c(3,3,3,0))
# ggplot() + #portfolio.points, aes(x = sd, y = mean, color = ETF, shape = Specific))
# geom_point(data = portfolio.points, aes(sd,mean)) +
#   geom_point(data = ETF.points, aes(sd, mean, color = ETF)) +
# geom_point (data = specific.points, aes(sd, mean, shape = label, size = 1))+
# geom_abline(intercept = future.annualised.risk.free.rate, slope =(specific.points[2, 1] - future.annualised.risk.free.rate)/specific.points[2, 2], linetype="dashed")+
# theme(plot.margin = margin(1, 1, 1, 1, "cm"))
#   #xlim(0, 0.35)+
# #ylim(0, 0.105)
```

## 3 Global Minimum Variance Portfolio
### We have modified the weights to create 3 different portfolios to cater to investors with different risk appetites. The first portfolio will be the Global Minimum Variance Portfolio(GVMP) the portfolio with the lowest Risk. It is weighted to give the least risk out of our holdings, catering to investors whose preferences lie in safe investments with minimal risk.

```{r GMVP, echo=FALSE}
#Portfolio with the lowest Risk - Global Minimum Variance Portfolio
gmvP <- minvariancePortfolio(myret, Spec, constraints = "maxW[1:16] = 0.4")
gmv.w <- getWeights(gmvP)

weights1 <- data.frame(gmv.w)
gmvpW1_draft <- round(subset(weights1, gmv.w*100 > 0.001),3)
assets <- colnames(getWeights(mymvf))
assets_names <- row.names(gmvpW1_draft)
gmvpPdf <- weights1 %>% rename(weights = `gmv.w`) 
gmvpPdf <- gmvpPdf  %>% mutate(Assets = rownames(gmvpPdf ))
###############################################
#Pie Chart for GMVP Weights

#Colours
weightColours <- brewer.pal(9, "YlGnBu") 


countryColours <- brewer.pal(5, "Pastel1") 


assetClassColours <- brewer.pal(5, "Pastel2") 


piepercent <- assets_names %>% 
  paste(",",sep ="") %>% 
  paste(100*as.vector(unlist(gmvpW1_draft))) %>% 
  paste("%",sep = "")

#pie(as.vector(unlist(gmvpW1_draft)), labels = piepercent, main = "Piechart of GMVP portfolio weights", col = weightColours, border = "white")
#legend("topright",assets_names, cex = 1, fill = colour, title = "Assets", bg='lightblue')

par(mar = c(1, 1, 1, 1)) # bltr

pie(
  as.vector(unlist(gmvpW1_draft)), 
  edges = 200, 
  radius = 0.8,
  clockwise = TRUE, # IMPORTANT
  angle = 45, 
  col = weightColours,
  border = "white",
  labels = piepercent, # NEVER DISPLAY OVERLAPPING LABELS
  main = "GMVP Portfolio Weights",
  cex = 0.8
)

legend(
  x = 1, # DELIBERATE POSITION
  y = 1, # DELIBERATE POSITION
  inset = .05, 
  legend = assets_names, 
  fill = weightColours,
  horiz = FALSE,
  cex = 0.7, # PROPER PARAMETER FOR TEXT SIZE
  text.width = 0.7, # SET THE BOX WIDTH
  bty="n" #No border
)

#################################################################################################################

#Sorting of country and type of investment into dataframe for each ETF
assetNames <- as.data.frame(colnames(ETFfxReturns))
assetNames <- as.data.frame(assetNames[-c(1:3),]) %>% rename(Assets = `assetNames[-c(1:3), ]`)

assetNames <- assetNames %>% mutate(`Asset Type` = case_when(
  Assets %in% c("AGG US Equity", "SCHP US Equity", "VCSH US Equity", "BNDX US Equity", "VWOB US Equity") ~ "Bonds", 
  Assets %in% c( "1306 JT Equity", "VOO US Equity", "VO US Equity", "VSS US Equity", "VGK US Equity",  "VWO US Equity") ~ "Equity", 
  Assets %in% c("1343 JT Equity","VNQ US Equity", "VNQI US Equity") ~ "Real Estate",
  Assets %in% c("IAU US Equity","BCI US Equity")~ "Gold & Commodities"))

assetNames <- assetNames %>% mutate(`Country` = case_when(
  Assets %in% c("AGG US Equity", "SCHP US Equity", "VCSH US Equity","VOO US Equity", "VO US Equity","VNQ US Equity") ~ "US",
  Assets %in% c("1306 JT Equity", "1343 JT Equity") ~ "Japan",
  Assets %in% c("BNDX US Equity", "VWOB US Equity",  "VSS US Equity", "VGK US Equity",  "VWO US Equity", "VNQI US Equity","IAU US Equity","BCI US Equity") ~ "Worldwide"))

###################################################################################################################

#Country & Asset Class Pie Chart
gmvpCountry <- cbind(assetNames, gmvpPdf$weights * 100) %>% rename(weights = `gmvpPdf$weights * 100`) %>% group_by(Country) %>% summarise(`Percentage Invested` = sum(weights))

colour <- rainbow(16)
piepercent <- gmvpCountry$Country %>% 
  paste(",",sep ="") %>% 
  paste(round(gmvpCountry$`Percentage Invested`,1)) %>% 
  paste("%",sep = "")

pie(gmvpCountry$`Percentage Invested`, labels = piepercent, main = "Countries Invested in the Global Minimum Variance Portfolio", col = countryColours, border = "white")
legend("topright",gmvpCountry$Country, cex = 0.8,
   fill = countryColours, bty="n")

gmvpAssetType <- cbind(assetNames, gmvpPdf$weights * 100) %>% rename(weights = `gmvpPdf$weights * 100`) %>% group_by(`Asset Type`) %>% summarise(`Percentage Invested` = sum(weights))

colour <- rainbow(16)
piepercent <- gmvpAssetType$`Asset Type` %>% 
  paste(",",sep ="") %>% 
  paste(round(gmvpAssetType$`Percentage Invested`, 1)) %>% 
  paste("%",sep = "")

pie(gmvpAssetType$`Percentage Invested`, labels = piepercent, main = "Types of Assets Invested in the Global Minimum Variance Portfolio", col = assetClassColours, border = "white")
legend("topright",gmvpAssetType$`Asset Type`, cex = 0.75,
   fill = assetClassColours,bty="n")

#########################################################################################################################
#Bar plot
# ggplot(data= gmvpW1_draft , aes(x=assets_names , y=gmv.w, fill=assets_names)) +
  # geom_bar(stat="identity", position=position_dodge(),colour="black") +
  # geom_text(aes(label=sprintf("%.02f %%",gmv.w*100)),
            # position=position_dodge(width=0.9), vjust=-0.25, check_overlap = TRUE) +
  # ggtitle("Minimum Variance Portfolio Optimal Weights")+ theme(plot.title = element_text(hjust = 0.5)) +
  # labs(x= "Assets", y = "Weight (%)") +
  # guides(fill = guide_legend(title = "Assets"))

```

## 4 Tangency Portfolio
### The second portfolio is the Tangency portfolio.

### This portfolio is weighted to maximise the portfolio’s Sharpe Ratio. This will provide the most balanced portfolio in terms of risk and returns. In comparision to the other portfolios, the amount of risk in this portfolio will be classified as medium.

```{r Tangent Portfolio, echo=FALSE}
#Tangency portfolio - HighestSharpe's Slope
tanP <- tangencyPortfolio(myret, Spec.rf, constraints = "maxW[-c(6, 1, 4, 3,10, 14, 7, 5)]=0.00" )
# get weights for tangency portfolio
tan.w <- round(getWeights(tanP), 3)
#Pie chart of the weights for the Tangency Portfolio
#weightsPie(tanP, box = FALSE)
tanwt1 <- data.frame(tan.w)
tanwt1_draft <- subset(tanwt1, tan.w*100 > 0.001)
assets_draft <- row.names(tanwt1_draft)

tanPdf <- tanwt1 %>% rename(weights = `tan.w`) 
tanPdf <- tanPdf  %>% mutate(Assets = rownames(tanPdf ))
################################################################
#Pie Chart for Tangency Portfolio

#setting colour
colour <- rainbow(8)

#Making the names of the labels
piepercent <- assets_draft %>% 
  paste(",",sep ="") %>% 
  paste(100*as.vector(unlist(tanwt1_draft))) %>% 
  paste("%",sep = "")

#pie chart weight
#pie(as.vector(unlist(tanwt1_draft)), labels = piepercent, main = "Tangency Portfolio weights", col = weightColours, border = "white")
#legend("top",assets_draft, cex = 0.5, fill = colour, title = "Assets", bg='lightblue')
par(mar = c(1, 1, 1, 1))

pie(
  as.vector(unlist(tanwt1_draft)), 
  edges = 200, 
  radius = 0.8,
  clockwise = TRUE, # IMPORTANT
  angle = 45, 
  col = weightColours,
  border = "white",
  labels = piepercent, # NEVER DISPLAY OVERLAPPING LABELS
  main = "Tangency Portfolio Weights",
  cex = 0.8
)

legend(
  x = 1, # DELIBERATE POSITION
  y = 0.4, # DELIBERATE POSITION
  inset = .05, 
  legend = assets_draft, 
  fill = weightColours,
  horiz = FALSE,
  cex = 0.7, # PROPER PARAMETER FOR TEXT SIZE
  text.width = 0.7, # SET THE BOX WIDTH
  bty="n" #No border
)  
###################################################################################################################

#Country & Asset Class Pie Chart
tanCountry <- cbind(assetNames, tanPdf$weights * 100) %>% rename(weights = `tanPdf$weights * 100`) %>% group_by(Country) %>% summarise(`Percentage Invested` = sum(weights))

colour <- rainbow(16)
piepercent <- tanCountry$Country %>% 
  paste(",",sep ="") %>% 
  paste(round(tanCountry$`Percentage Invested`,1)) %>% 
  paste("%",sep = "")

pie(tanCountry$`Percentage Invested`, labels = piepercent, main = "Countries Invested in the Tangency Portfolio",col = countryColours, border = "white")
legend("topright",tanCountry$Country, cex = 0.8,
   fill = countryColours, bty="n")

tanAssetType <- cbind(assetNames, tanPdf$weights * 100) %>% rename(weights = `tanPdf$weights * 100`) %>% group_by(`Asset Type`) %>% summarise(`Percentage Invested` = sum(weights))

colour <- rainbow(16)
piepercent <- tanAssetType$`Asset Type` %>% 
  paste(",",sep ="") %>% 
  paste(round(tanAssetType$`Percentage Invested`, 1)) %>% 
  paste("%",sep = "")

pie(tanAssetType$`Percentage Invested`, labels = piepercent, main = "Types of Assets Invested in the Tangency Portfolio", col = assetClassColours, border = "white")
legend("topright",tanAssetType$`Asset Type`, cex = 0.75,
   fill = assetClassColours, bty="n")

#########################################################################################################################
```

## 5 Max Returns Portfolio 
### The last portfolio, is the Max returns Portfolio. It is catered for investors who are willing to take on higher risk with their holdings.

### The Maximum returns portfolio is weighted to have the highest returns but also the highest risk from our chosen holdings. This portfolio is suited for investors with high risk tolerance.

```{r Max returns Portfolio, echo=FALSE}
ret2 = ETFfxReturns[,-(1:3)]  #excluding dates
mu1 = t(annualised.hist.geo.mean)[-c(1,2),]#colMeans(ret2)  #mean returns
na1 = ncol(ret2)  #number of assets
varc1 = cov(ret2)

riskp1 = NULL  #vector to store risk
retp1 = NULL  #vector to store returns

w = c(0,0,0,8.4087, 16.2471, 5.0822, 48.3172, 4.7284, 0,4.2494, 3.1067, 0,0, 9.8862,0,0)  #max p weights
r1 = t(w) %*% mu1 #t(annualised.hist.geo.mean)[-c(1,2),]   #matrix multiplication
sd1 = t(w) %*% annualised.covariance.matrix %*% w #t(w) %*% varc1 %*% w
retp1 = rbind(retp1, r1)
riskp1 = rbind(riskp1, sqrt(sd1))

#list of ETFs
maxP.ETFs <- c("VWOB US Equity", "1306 JT Equity", "VOO US Equity", "VO US Equity", "VNQI US Equity", "VGK US Equity","BNDX US Equity", "VWO US Equity")

#Weightage of ETFS (1.dp)
maxP.weights <-  c(16.2, 5.1, 48.3, 4.7, 9.9, 4.3, 8.4, 3.1)

###########################################################################################
#Pie Chart for MaxP

piepercent <- maxP.ETFs %>% 
  paste(",",sep ="") %>% 
  paste(maxP.weights) %>% 
  paste("%",sep = "")

#pie(maxP.weights, labels = piepercent, main = "Max Returns Portfolio weights", col = weightColours, border = "white")
#legend("top",assets_draft, cex = 0.5, fill = colour, title = "Assets", bg='lightblue')

par(mar = c(1, 1, 1, 1))

pie(
  maxP.weights, 
  edges = 200, 
  radius = 0.8,
  clockwise = TRUE, # IMPORTANT
  angle = 45, 
  col = weightColours,
  border = "white",
  labels = piepercent, # NEVER DISPLAY OVERLAPPING LABELS
  main = "Max Returns Portfolio weights",
  cex = 0.8
)

legend(
  x = 1, # DELIBERATE POSITION
  y = 0, # DELIBERATE POSITION
  inset = .05, 
  legend = maxP.ETFs, 
  fill = weightColours,
  horiz = FALSE,
  cex = 0.7, # PROPER PARAMETER FOR TEXT SIZE
  text.width = 0.7, # SET THE BOX WIDTH
  bty="n" #No border
)  
###################################################################################################################
maxPdf <- data.frame(weights = w, Assets = rownames(tanPdf))

#Country & Asset Class Pie Chart
maxPCountry <- cbind(assetNames, maxPdf$weights) %>% rename(weights = `maxPdf$weights`) %>% group_by(Country) %>% summarise(`Percentage Invested` = sum(weights))

piepercent <- maxPCountry$Country %>% 
  paste(",",sep ="") %>% 
  paste(round(maxPCountry$`Percentage Invested`,1)) %>% 
  paste("%",sep = "")

pie(maxPCountry$`Percentage Invested`, labels = piepercent, main = "Countries Invested in the Maximum Returns Portfolio", col = countryColours, border = "white")
legend("topright",maxPCountry$Country, cex = 0.8,
   fill = countryColours, bty="n")

maxPAssetType <- cbind(assetNames, maxPdf$weights) %>% rename(weights = `maxPdf$weights`) %>% group_by(`Asset Type`) %>% summarise(`Percentage Invested` = sum(weights))

colour <- rainbow(16)
piepercent <- maxPAssetType$`Asset Type` %>% 
  paste(",",sep ="") %>% 
  paste(round(maxPAssetType$`Percentage Invested`, 1)) %>% 
  paste("%",sep = "")

pie(maxPAssetType$`Percentage Invested`, labels = piepercent, main = "Types of Assets Invested in the Maximum Returns Portfolio", col = assetClassColours, border = "white")
legend("topright",maxPAssetType$`Asset Type`, cex = 0.75,
   fill = assetClassColours, bty="n")

#####################################################################################################################

```

## 6 Equal Weight Portfolio

### We also showed the equal weights portfolio. For investors who are curious how the portfolio would look like if we were to invest equally in the securities selected.

```{r ewP, echo=FALSE}
ewSpec <- Spec
setWeights(ewSpec) <- rep(1/(ncol.rets - 3), times = (ncol.rets-3))
ewP <- feasiblePortfolio(myret, spec = ewSpec, constraints = "LongOnly")
getTargetReturn(ewP)
getTargetRisk(ewP)
ewP@portfolio@portfolio$weights
ewPdf <- as.data.frame(ewP@portfolio@portfolio$weights) %>% rename(weights = `ewP@portfolio@portfolio$weights`) 
ewPdf <- ewPdf %>% mutate(Assets = rownames(ewPdf)) 
# ggplot(ewPdf, aes(x = Assets, y = weights, fill = Assets))  + geom_bar(stat = "identity")+ theme_classic() + coord_flip() + theme(legend.position = "none", panel.grid.major = element_blank())

#pie(ewPdf$weights, labels = piepercent, main = "Piechart of equal-weighted portfolio weights", col = colour)
#legend("topright",ewPdf$Assets, cex = 1, fill = colour, title = "Assets", bg='lightblue')

#Pie Chart for ewP

piepercent <- ewPdf$Assets %>% 
  paste(",",sep ="") %>% 
  paste(100*as.vector(ewPdf$weights)) %>% 
  paste("%",sep = "")

#pie(maxP.weights, labels = piepercent, main = "Max Returns Portfolio weights", col = weightColours, border = "white")
#legend("top",assets_draft, cex = 0.5, fill = colour, title = "Assets", bg='lightblue')

par(mar = c(1, 1, 1, 1))

pie(
  ewPdf$weights, 
  edges = 200, 
  radius = 0.8,
  clockwise = TRUE, # IMPORTANT
  angle = 45, 
  col = weightColours,
  border = "white",
  labels = piepercent, # NEVER DISPLAY OVERLAPPING LABELS
  main = "1/N Portfolio Weights",
  cex = 0.8
)

# legend(
#   ncol = 2,
#   x = 1, # DELIBERATE POSITION
#   y = 0.5, # DELIBERATE POSITION
#   inset = .05, 
#   legend = ewPdf$Assets, 
#   fill = weightColours,
#   horiz = FALSE,
#   cex = 0.7, # PROPER PARAMETER FOR TEXT SIZE
#   text.width = NULL, # SET THE BOX WIDTH
#   bty="n" #No border
# )  


ewpCountry <- cbind(assetNames, ewPdf$weights * 100) %>% rename(weights = `ewPdf$weights * 100`) %>% group_by(Country) %>% summarise(`Percentage Invested` = sum(weights))

piepercent <- ewpCountry$Country %>% 
  paste(",",sep ="") %>% 
  paste(ewpCountry$`Percentage Invested`) %>% 
  paste("%",sep = "")

pie(ewpCountry$`Percentage Invested`, labels = piepercent, main = "Countries Invested in the Equal Weights Portfolio", col = countryColours, border = "white")
legend("topright",ewpCountry$Country, cex = 0.8,
   fill = countryColours, bty="n")

ewpAssetType <- cbind(assetNames, ewPdf$weights * 100) %>% rename(weights = `ewPdf$weights * 100`) %>% group_by(`Asset Type`) %>% summarise(`Percentage Invested` = sum(weights))

piepercent <- ewpAssetType$`Asset Type` %>% 
  paste(",",sep ="") %>% 
  paste(ewpAssetType$`Percentage Invested`) %>% 
  paste("%",sep = "")

pie(ewpAssetType$`Percentage Invested`, labels = piepercent, main = "Types of Assets Invested in the Equal Weights Portfolio", col = assetClassColours, border = "white")
legend("bottomright",ewpAssetType$`Asset Type`, cex = 0.75,
   fill = assetClassColours, bty="n")

```

```{r overall returns and risks, echo=FALSE}

port1 <- c("Global Minimum Variance", getTargetReturn(gmvP)[1] * 100, getTargetRisk(gmvP)[1] * 100, (getTargetReturn(gmvP)[1] - future.annualised.risk.free.rate) / getTargetRisk(gmvP)[1])
port2 <- c("Tangency", getTargetReturn(tanP)[1] * 100, getTargetRisk(tanP)[1] * 100, (getTargetReturn(tanP)[1] - future.annualised.risk.free.rate) / getTargetRisk(tanP)[1])
port3 <- c("Maximum Returns", retp1 * 100, riskp1 * 100, (retp1 - future.annualised.risk.free.rate) / riskp1)
port4 <- c("Equal Weights", getTargetReturn(ewP)[1] * 100, getTargetRisk(ewP)[1] * 100, (getTargetReturn(ewP)[1] - future.annualised.risk.free.rate) / getTargetRisk(ewP)[1])

portfolioSummary <- as.data.frame(rbind(port1, port2, port3, port4))

rownames(portfolioSummary) <- portfolioSummary$V1 
portfolioSummary <- portfolioSummary[,-1] 
colnames(portfolioSummary) <- c("Portfolio Returns (%)", "Portfolio Risk(%)", "Sharpe Ratio") 

kable(portfolioSummary)

```


```{r backtest, echo=FALSE}
cumulative_returns_func <- function(weights, data, nrows) {
  starting = 1000
  #252/12 = 21, we rebalance every 21 days 
  cumulative_returns <- data.frame(
    matrix(ncol = ncol.rets-3, 
           nrow = nrows+1))
  cumulative_returns[1,] = 1000*weights
  for(i in 1: nrows) { 
    for (j in 1:16) { 
      cumulative_returns[i+1, j] = cumulative_returns[i, j] * 
        (1 + data[i, j + 3])
    }
  if(i%%21 == 0) {
    sum1 = sum(cumulative_returns[i+1, ])
    cumulative_returns[i+1, ] = sum1*weights
    }
  }
  return(cumulative_returns)
}

gmvp.weights = data.frame(t(data.frame(getWeights(gmvP))))
tanp.weights = data.frame(t(data.frame(getWeights(tanP))))
maxp.weights = data.frame(0,0,0,0.084087, 0.162471, 0.050822, 0.483172, 0.047284, 0, 0.042494, 0.031067, 0,0, 0.098862,0,0)
colnames(maxp.weights) <- c("AGG US Equity", "SCHP US Equity", "VCSH US Equity", "BNDX US Equity", "VWOB US Equity", "1306 JT Equity", "VOO US Equity", "VO US Equity", "VSS US Equity", "VGK US Equity", "VWO US Equity", "1343 JT Equity", "VNQ US Equity", "VNQI US Equity", "IAU US Equity", "BCI US Equity")
ewp.weights = data.frame(0.0625,0.0625,0.0625,0.0625, 0.0625, 0.0625, 0.0625, 0.0625, 0.0625, 0.0625, 0.0625, 0.0625, 0.0625, 0.0625, 0.0625, 0.0625)
colnames(ewp.weights) <- c("AGG US Equity", "SCHP US Equity", "VCSH US Equity", "BNDX US Equity", "VWOB US Equity", "1306 JT Equity", "VOO US Equity", "VO US Equity", "VSS US Equity", "VGK US Equity", "VWO US Equity", "1343 JT Equity", "VNQ US Equity", "VNQI US Equity", "IAU US Equity", "BCI US Equity")

#20 years backtest
ETFfxReturns_20Y <- ETFfxReturns[122:5340, ]

cumulative.returns.gmvp <- cumulative_returns_func(gmvp.weights, ETFfxReturns_20Y, 5219)
cumulative.returns.tanp <- cumulative_returns_func(tanp.weights, ETFfxReturns_20Y, 5219)
cumulative.returns.maxp <- cumulative_returns_func(maxp.weights, ETFfxReturns_20Y, 5219)
cumulative.returns.ewp <- cumulative_returns_func(ewp.weights, ETFfxReturns_20Y, 5219)

ETFfxReturns_20Y$mktProd <- ETFfxReturns_20Y$mkt + 1

ret <- c(ETFfxReturns_20Y[1:5219, 1])
rs_gmvp <- rowSums(cumulative.returns.gmvp[2:5220, 1:16])/1000
rs_tanp <- rowSums(cumulative.returns.tanp[2:5220, 1:16])/1000
rs_maxp <- rowSums(cumulative.returns.maxp[2:5220, 1:16])/1000
rs_ewp <- rowSums(cumulative.returns.ewp[2:5220, 1:16])/1000
benchmark <- cumprod(ETFfxReturns_20Y$mktProd)


df <- data.frame(ret, rs_gmvp, rs_tanp, rs_maxp, benchmark, rs_ewp)
plot(x = as.Date(df$x), y = df$rs_gmvp, type = 'l', col = 'red', ylim = c(0.5, 6), main = "Portfolios Backtesting - 20 Years", xlab = "Date", ylab = "Cumulative Returns")
lines(x = as.Date(df$x), y = df$rs_tanp, type = 'l', col = 'blue')
lines(x = as.Date(df$x), y = df$rs_maxp, type = 'l', col = 'green3')
lines(x = as.Date(df$x), y = df$benchmark, type = 'l', col = 'orange')
lines(x = as.Date(df$x), y = df$rs_ewp, type = 'l', col = 'black')
legend("topleft", legend = c("Low", "Mid", "High", "mkt", "Equal Weighted"), col = c("red", "blue", "green3", "orange", "black"), lty=1:2, cex=0.8)

#10 years backtest
ETFfxReturns_10Y <- ETFfxReturns[2731:5340, ]

cumulative.returns.gmvp_10Y <- cumulative_returns_func(gmvp.weights, ETFfxReturns_10Y, 2610)
cumulative.returns.tanp_10Y <- cumulative_returns_func(tanp.weights, ETFfxReturns_10Y, 2610)
cumulative.returns.maxp_10Y <- cumulative_returns_func(maxp.weights, ETFfxReturns_10Y, 2610)
cumulative.returns.ewp_10Y <- cumulative_returns_func(ewp.weights, ETFfxReturns_10Y, 2610)

ETFfxReturns_10Y$mktProd <- ETFfxReturns_10Y$mkt + 1

ret_10Y <- c(ETFfxReturns_10Y[1:2610, 1])
rs_gmvp_10Y <- rowSums(cumulative.returns.gmvp_10Y[2:2611, 1:16])/1000
rs_tanp_10Y <- rowSums(cumulative.returns.tanp_10Y[2:2611, 1:16])/1000
rs_maxp_10Y <- rowSums(cumulative.returns.maxp_10Y[2:2611, 1:16])/1000
rs_ewp_10Y <- rowSums(cumulative.returns.ewp_10Y[2:2611, 1:16])/1000
benchmark_10Y <- cumprod(ETFfxReturns_10Y$mktProd)


df <- data.frame(ret_10Y, rs_gmvp_10Y, rs_tanp_10Y, rs_maxp_10Y, benchmark_10Y, rs_ewp_10Y)
plot(x = as.Date(df$x), y = df$rs_gmvp_10Y, type = 'l', col = 'red', ylim = c(0.5, 6), main = "Portfolios Backtesting - 10 Years", xlab = "Date", ylab = "Cumulative Returns")
lines(x = as.Date(df$x), y = df$rs_tanp_10Y, type = 'l', col = 'blue')
lines(x = as.Date(df$x), y = df$rs_maxp_10Y, type = 'l', col = 'green3')
lines(x = as.Date(df$x), y = df$benchmark_10Y, type = 'l', col = 'orange')
lines(x = as.Date(df$x), y = df$rs_ewp_10Y, type = 'l', col = 'black')
legend("topleft", legend = c("Low", "Mid", "High", "mkt", "Equal Weighted"), col = c("red", "blue", "green3", "orange", "black"), lty=1:2, cex=0.8)

#5 years backtest
ETFfxReturns_5Y <- ETFfxReturns[4036:5340, ]

cumulative.returns.gmvp_5Y <- cumulative_returns_func(gmvp.weights, ETFfxReturns_5Y, 1305)
cumulative.returns.tanp_5Y <- cumulative_returns_func(tanp.weights, ETFfxReturns_5Y, 1305)
cumulative.returns.maxp_5Y <- cumulative_returns_func(maxp.weights, ETFfxReturns_5Y, 1305)
cumulative.returns.ewp_5Y <- cumulative_returns_func(ewp.weights, ETFfxReturns_5Y, 1305)

ETFfxReturns_5Y$mktProd <- ETFfxReturns_5Y$mkt + 1

ret_5Y <- c(ETFfxReturns_5Y[1:1305, 1])
rs_gmvp_5Y <- rowSums(cumulative.returns.gmvp_5Y[2:1306, 1:16])/1000
rs_tanp_5Y <- rowSums(cumulative.returns.tanp_5Y[2:1306, 1:16])/1000
rs_maxp_5Y <- rowSums(cumulative.returns.maxp_5Y[2:1306, 1:16])/1000
rs_ewp_5Y <- rowSums(cumulative.returns.ewp_5Y[2:1306, 1:16])/1000
benchmark_5Y <- cumprod(ETFfxReturns_5Y$mktProd)


df <- data.frame(ret_5Y, rs_gmvp_5Y, rs_tanp_5Y, rs_maxp_5Y, benchmark_5Y, rs_ewp_5Y)
plot(x = as.Date(df$x), y = df$rs_gmvp_5Y, type = 'l', col = 'red', ylim = c(0.5, 2), main = "Portfolios Backtesting - 5 Years", xlab = "Date", ylab = "Cumulative Returns")
lines(x = as.Date(df$x), y = df$rs_tanp_5Y, type = 'l', col = 'blue')
lines(x = as.Date(df$x), y = df$rs_maxp_5Y, type = 'l', col = 'green3')
lines(x = as.Date(df$x), y = df$benchmark_5Y, type = 'l', col = 'orange')
lines(x = as.Date(df$x), y = df$rs_ewp_5Y, type = 'l', col = 'black')
legend("topleft", legend = c("Low", "Mid", "High", "mkt", "Equal Weighted"), col = c("red", "blue", "green3", "orange", "black"), lty=1:2, cex=0.8)
```

```{r rebalancing, echo=FALSE}
# gmvp.weights = data.frame(t(data.frame(getWeights(gmvP))))
# starting = 1000
# #252/12 = 21, we rebalance every 21 days 
# cumulative.returns <- data.frame(
#   matrix(ncol = ncol.rets-3, 
#          nrow = nrow.rets+1))
# cumulative.returns[1,] = 1000*gmvp.weights
# #cumalative.return = t(cumulative.returns)
# for(i in 1: nrow.rets) { 
#   for (j in 1:16) { 
#     cumulative.returns[i+1, j] = cumulative.returns[i, j] * 
#       (1 + ETFfxReturns[i, j + 3])
#   }
#   if(i%%21 == 0) {
#     sum1 = sum(cumulative.returns[i+1, ])
#     cumulative.returns[i+1, ] = sum1*gmvp.weights
#     }
# }
```

\newpage
# Appendix

## Historical Statistics
We include a table calculating the historical annualized geometric return $(\mu)$, variance $(\sigma^2)$, and standard deviation $(\sigma)$ values of the market portfolio, risk-free asset and individual ETFs over the defined period. 
\
\
**Note:** we used the average number of trading days, 252 days, for the purpose of annualization.
\
\
```{r print historical statistics, echo=FALSE}
#Change the label for mkt and rf
annualised.hitorical.statistics <- data.frame(
  matrix(ncol = 3, nrow = ncol.rets-1))
colnames(annualised.hitorical.statistics) = c("Geometric return", 
                                              "Variance", 
                                              "Standard deviation")
annualised.hitorical.statistics$`Geometric return` = unlist(annualised.hist.geo.mean)
annualised.hitorical.statistics$`Variance` = unlist(annualised.hist.var)
annualised.hitorical.statistics$`Standard deviation` = unlist(annualised.hist.sd)

annualised.hitorical.statistics = round(annualised.hitorical.statistics, 3)
rownames(annualised.hitorical.statistics) = c("Market", "Risk-Free", colnames(ETFfxReturns)[-(1:3)])

kable(annualised.hitorical.statistics,caption = "Historical Statistics")
```

\newpage
## Inputs for Portfolio Optimisation

In order to perform portfolio optimization, we obtained the expected annualized return, as well as the covariance matrix.

### Expected Annualised Return

To calculate the expected annualized return, we used capital asset pricing model (CAPM). This is given by 

<p class="text-center">$\mu_i=R^f + \beta_i*MRP$</p>

#### Risk-Free Rate

For our risk-free rate, we used 0.1%. We obtained this figure by calculating the annualized historical geometric mean for our risk-free asset over the period mentioned above. This is a reasonable estimate given the dovish stance of the Bank of Japan.

#### Market Risk Premium
For our market risk premium (MRP), we used 6%. 

#### Covariance Matrix
To calculate the covariance matrix, we used the historical values provided.
\
\

```{r print beta values expected miu and covariance matrix, echo=FALSE}
df.toprint <- data.frame(
  matrix(ncol = 2, nrow = ncol.rets-3))
rownames(df.toprint) = c(colnames(ETFfxReturns)[-(1:3)])
colnames(df.toprint) = c("Beta", "Expected Annualised Return")

df.toprint$Beta = unlist(beta.df)
df.toprint$`Expected Annualised Return` = unlist(annualised.expected.miu)
df.toprint = round(df.toprint,3)
kable(df.toprint, caption = "Beta and Expected Annualised Return")

#Don't need to print the covariance matrix
```


```{r sharpe plot, echo=FALSE}

np = 400  #number of portfolios
ret = ETFfxReturns[,-(1:3)]  #excluding dates
mu = t(annualised.hist.geo.mean)[-c(1,2),]#colMeans(ret2)  #mean returns
na = ncol(ret2)  #number of assets
varc = cov(ret2)

#annualised.covariance.matrix = var(ETFfxReturns[,-(1:3)]) * 252

riskp = NULL  #vector to store risk
retp = NULL  #vector to store returns

for (i in 1:np) {
    w = diff(c(0, sort(runif(na - 1)), 1))  # random weights
    r = t(w) %*% mu #t(annualised.hist.geo.mean)[-c(1,2),]   #matrix multiplication
    sd = t(w) %*% annualised.covariance.matrix %*% w #t(w) %*% varc1 %*% w
    retp = rbind(retp, r)
    riskp = rbind(riskp, sqrt(sd))
}

# create a data frame of risk and return
d_p1 = data.frame(Ret = retp, Risk = riskp)
d_p1 = d_p1 %>% mutate(SharpeRatio = (Ret - 0.001697914) / Risk)
p1 = ggplot(d_p1, aes(Risk, Ret, colour = SharpeRatio))
# scatter plot
p1 = p1 + geom_point()
# scatter plot with density and identified port risk return (highest
# lowest returns and min risk)
p1 + geom_point() + geom_hline(yintercept = c(max(d_p1$Ret), median(d_p1$Ret),
    min(d_p1$Ret)), colour = c("darkgreen", "darkgray", "darkred"), size = 1) +
    geom_vline(xintercept = d_p1[(d_p1$Risk == min(d_p1$Risk)), ][, 2]) +
    labs(colour = "Sharpe Ratio", x = "Portfolio Risk", y = "Portfolio Return",
        title = "Random Feasible Portfolios") + theme_bw() 




```


